Gaussian Process regression for astronomical time-series

### 2022-09-08 src/tex/ms.tex
[showyourwork] overleaf sync

@@

\begin{figure}[ht]
  \centering
  \script{GPR_PGM.ipynb}
  \includegraphics[width=\linewidth]{figures/GPR_PGM.pdf}
  \caption{Probabilistic Graphical Model (PGM) for GP regression (adapted from Figure 2.3 of \citealt{RW07} given observations $\mathbf{y}$ at inputs $\mathbf{t}$, and a prediction at test input $t_\star$. Dots represent fixed variables (inputs), grey circles represent observed variables white circles represent unknown (latent) variables. The thick thick horizontal bar indicates a set of fully connected nodes. In this example, the GP hyper-parameters (not shown) are treated as.}
  \label{fig:GPR_PGM}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=3in]{figures/RV_framework.pdf}
  \caption{Schematic of the GP framework of \citet{2015MNRAS.452.2269R} for modelling activity signals in RV data \suz{Figure will be updated with nicer version.}}
  \label{fig:RV_framework}
\end{figure}

>>>>

\begin{figure}[ht]
  \centering
  \includegraphics[width=\linewidth]{figures/GPR_workflow.pdf}
  \caption{The workflow.}
  \label{fig:GPR_workflow}
\end{figure}

@@

\begin{figure}[ht]
  \centering
  \script{GPR_PGM.ipynb}
  \includegraphics[width=\linewidth]{figures/GPR_PGM.pdf}
  \caption{Probabilistic Graphical Model (PGM) for GP regression (adapted from Figure 2.3 of \citealt{RW07} given observations $\mathbf{y}$ at inputs $\mathbf{t}$, and a prediction at test input $t_\star$. Dots represent fixed variables (inputs), grey circles represent observed variables white circles represent unknown (latent) variables. The thick thick horizontal bar indicates a set of fully connected nodes. In this example, the measurement uncertainties $\boldsymbol{\sigma}$ and the GP hyper-parameters (not shown) are treated as known (fixed).}
  \label{fig:GPR_PGM}
\end{figure}

@@

\begin{figure}[ht]
  \includegraphics[width=\linewidth]{figures/RV_framework.pdf}
  \caption{Schematic of the multi-dimensional GP framework of \citet{2015MNRAS.452.2269R} for modelling activity signals in RV data. The observed RVs (shown as orange points with error bars in the bottom right panel) are modelled alongside observations of activity indicators extracted from the spectra or line profiles (orange points with error bars in the bottom left and bottom middle panels). In all these time-series, the activity signal (shown by the black line in each panel) is modelled as a linear combination of an unobserved (latent) GP, shown in the top-left panel, and its first time-derivative, shown in the top middle panel. In addition, the Keplerian signal(s) of putative planet(s) (the sum of which is shown by the blue lines in the top right and bottom right panels) contribute to the RVs but not to the activity indicators. This hierarchical model is implemented in a Bayesian framework, sampling over all the hyper-parameters listed in the blue boxes (subject to appropriate priors) to derive posteriors over the hyper-parameters of interest or evaluating the evidence for models with different numbers of planets. \suz{Ideally we would replace this static figure with a dynamically generated one, but failing that we might add the Annual Reviews graphics editors to help improve it.}}
  \label{fig:RV_framework}
\end{figure}
